Think deep for reef resilience

### 2025-09-25 paper/paper_draft.qmd
Reorder sections
Scenario modelling section ends on "clustered based on temporal behaviour" and then jumps to connectivity modelling, then jumps back to time series clustering.

Reordered for a more logical flow.

All data preparation, modelling and analyses were performed using the Julia programming
language (The Julia Project; https://julialang.org/; [@bezanson2017]), with visualisations
created using the Makie ecosystem [@danisch2021].

>>>>

All data preparation, modelling and analyses were performed using the Julia programming
language (The Julia Project; https://julialang.org/; [@bezanson2017]), with visualisations
created using the Makie plotting ecosystem [@danisch2021].
